A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-30 paper/paper.tex
paper: add author emails

\title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
\author{\IEEEauthorblockN{Hugo Herbelin \\ and Ramkumar Ramachandra} \IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}

>>>>

\title{A parametricity-based formalization of semi-simplicial and semi-cubical sets}
\author{\IEEEauthorblockN{Hugo Herbelin \texttt{<Hugo.Herbelin@inria.fr>} \\ and Ramkumar Ramachandra \texttt{<r@artagnon.com>}}\IEEEauthorblockA{Université Paris Cité, Inria, CNRS, IRIF, Paris}}
